---
title: "SteroidDoseStudy"
author: "Sun Gyu Chae and Yeesuk Kim"
date: "2022-01-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
This package generates dose study package for user-defined index drugs by utilizing R shiny GUI and determines the cutoff level of maximum AUC using logistic regression, support vector machine and one-class support vector machine by utilizing generalized propensity score analysis. 

## Features
This package automatically generates dose study package by using user-defined..
1. 4 target drug groups for study
2. Target prerequsite condition group 
3. Target outcome condition group
4. Drug potency generalization by applying weights
5. Transformation of cumulative drug usage (log, exponential)

#How to run
==========
1. After cloning ths repository, double click Rproj file to launch package, and open 'app.r'

2. In R Studio application, please click 'Run App' button on top right in the script panel.

3. Follow the insructions below. 

3.1. Supply user-defined drug groups and condition groups for the study.

3.2. If drug potency varies among drug groups, apply weights for generalization of potency among drug groups.

3.3. If it is believed that transformation of variable (cumulative drug usage) is required, please select drug transformation measures.

3.4. Finally, click get package button in sidebar to access your package.

3.5. To operate your study, follow instructions below:
Add below details of your CDM database in "CodeToRun.R"
```{r}
cdmDatabaseSchema <- "" ## server_database.server_scheme 
resultsDatabaseSchema <- ""

connectionDetails <- DatabaseConnector::createConnectionDetails(dbms = "", #"postgresql"
                                                                server = "",
                                                                user = "",
                                                                password = "",
                                                                port = NULL)
```

When error caused by missing JDBC drivers, download required JDBC drivers using:
```{r}
Sys.setenv("DATABASECONNECTOR_JAR_FOLDER" = "C:/JDBC") 
downloadJdbcDrivers() #postgresql, redshift .. etc
```

4. Congratulations. All done 

